\subsection{Equivalence Relations}
The structural congruence of processes, denoted by the relation $\equiv$, allows us to express if two processes have the same structure. It is defined by the following rules.

\begin{align*}
    \tag{ParaIdentity}P&\equiv P\para 0\\
    \tag{ParaCommutative}\label{rule:ParaCommutative}P\para Q &\equiv Q\para P\\
    \tag{ParaAssociative}P\para (Q\para R)&\equiv (P\para Q)\para R
\end{align*}


\FloatBarrier

The equivalence of names, denoted by the relation $\equiv _N$, allows us to express if two names are the same. It is defined by the following rules.

\begin{align}
    \tag{DropAndQuote}\label{rule:DropAndQuote}\infrule{}{\quot{\drop{x}}\equiv _N x}
\end{align}

\noindent
The \ref{rule:DropAndQuote} rule states, that if $x$ is dropped, and then quoted, then it should stay name equivalent with $x$.

\begin{align}
    \tag{StructuralEquivalence}\label{rule:StructuralEquivalence}\infrule{P\equiv Q}{\quot{P} \equiv _N \quot{Q}}
\end{align}

\noindent
The \ref{rule:StructuralEquivalence} rule states, that if $P$ and $Q$ are structural congruent with each other, then the quoted $P$ and $Q$ are name equivalent with each other.

\FloatBarrier

\subsection*{Name substitution} The name substitution $P\{x/y\}$ denotes that every occurrence of the name $y$ in the process $P$ is substituted by the name $x$.

\subsection{Reduction Rules}
We make use of the following reduction rules.

\subsubsection{Base rules}
These are similar to the reduction rules of the rho-calculus as described in \citep{Meredith2005}. The only difference is the communication rule reflecting the syntax changes.

\begin{align}
    \tag{Comm} \infrule{x_0 \equiv_N x_1}{\lift{x_0}{M}\para\inp{x_1}{y}P\ra P\{M/y\}}&\\
    \tag{Parallel} \infrule{P\ra P'}{P\para Q\ra P'\para Q}&\\
    \tag{Equivalence} \infrule{P\equiv P'\quad P'\ra Q'\quad Q'\equiv Q}{P\ra Q}&
\end{align}

\FloatBarrier

\subsubsection{Rules for conditional processes}
The reduction rule of a given conditional process is decided by its boolean expression. These are evaluated using common boolean arithmetics.

\begin{align}
    & \infrule{\phi \ra \top}{[\phi]P\ra P} \tag{True}\\
    & \infrule{\phi \ra \bot}{[\phi]P\ra \nil} \tag{False}
\end{align}

The rules for boolean logic, "and", "or", and "negation", is shown here, under what condition it is evaluated to true (\ensuremath{\top}) and false (\ensuremath{\bot}).
\begin{align*}
    \infrule{\phi_1 \ra \top \quad \phi_2 \ra \top}{\phi_1 \wedge \phi_2 \ra \top}\tag{And True}\\
    \infrule{\phi_i \ra \bot}{\phi_1 \wedge \phi_2 \ra \bot} &\text{where}\ i\in \{1,2\}\tag{And False}\\
    \infrule{\phi_i \ra \top}{\phi_1 \vee \phi_2 \ra \top} &\text{where}\ i\in \{1,2\} \tag{Or True}\\
    \infrule{\phi_1 \ra \bot \quad \phi_2 \ra \bot}{\phi_1 \vee \phi_2 \ra \bot} \tag{Or False}\\
    \infrule{\phi \ra \bot}{\neg\phi \ra \top} \tag{Negate True}\\
    \infrule{\phi \ra \top}{\neg\phi \ra \bot} \tag{Negate False}\\
\end{align*}

The rules for arithmetic logic, equal to, greater than, etc., does not specify what happens if the terms are not comparable, like numbers and strings.


\begin{align*}
    \infrule{}{M_1 = M_2 \ra \top}& \text{if }M_1=M_2 \tag{Equal True}\\
    \infrule{}{M_1 = M_2 \ra \bot}& \text{if }M_1\neq M_2 \tag{Equal False}\\
    \infrule{}{M_1 \neq M_2 \ra \top}& \text{if }M_1\neq M_2 \tag{NotEqual True}\\
    \infrule{}{M_1 \neq M_2 \ra \bot}& \text{if }M_1= M_2 \tag{NotEqual False}\\
    \infrule{}{M_1 < M_2 \ra \top}& \text{if }M_1<M_2 \tag{Less True}\\
    \infrule{}{M_1 < M_2 \ra \bot}& \text{if }M_1\nless M_2 \tag{Less False}\\
    \infrule{}{M_1 > M_2 \ra \top}& \text{if }M_1>M_2 \tag{Greater True}\\
    \infrule{}{M_1 > M_2 \ra \bot}& \text{if }M_1\ngtr M_2 \tag{Greater False}\\
    \infrule{}{M_1 \leq M_2 \ra \top}& \text{if }M_1\leq M_2 \tag{Less Equal True}\\
    \infrule{}{M_1 \leq M_2 \ra \bot}& \text{if }M_1\nleq M_2 \tag{Less Equal False}\\
    \infrule{}{M_1 \geq M_2 \ra \top}& \text{if }M_1\geq M_2 \tag{Greater Equal True}\\
    \infrule{}{M_1 \geq M_2 \ra \bot}& \text{if }M_1\ngeq M_2 \tag{Greater Equal False}
\end{align*}


\FloatBarrier
\input{Sections/Syntax/replication.tex}

\input{Sections/Semantics/operations.tex}
