\section{Introduction}
The distributed algorithm blockchain has become very popular these years. The algorithm became widely known from the Bitcoin protocol, where it was used to create a decentralized cryptocurrency\citep{website:blockchain}. The blockchain consists of a chain of blocks, hence the name, where anyone in the network can add new blocks to the chain. To ensure that the blocks are valid consensus in the network has to be achieved. This is done with a consensus algorithm. Depending on the algorithm the process is different but they all have one property in common is that a large amount of the network has to agree and thereby give consensus of the validity of the new block, for it to be added to the chain.\\
Bitcoin is not the only implementation of the blockchain algorithm. Another example is the RChain protocol\citep{website:RChain}. The RChain is a blockchain algorithm currently in the descriptive phase designed to be written in the rho-lang, which is a concurrency-oriented programming language. The language is designed to easily translate rho-calculus to rho-lang\citep{website:rho-lang}, although in this article RChain is mainly used as an inspiration and also one of the reasons for using rho-calculus. The appendix of this article includes a rho-calculus implementation based on the naivechain, which is an example of a blockchain implementation\citep{naivechain}.\\

The rho-calculus is a very expressive calculus but for our own convenience, we choose to extend the calculus that can be read in section \ref{ch:rho-calculus}. The extensions were added to simplify our blockchain implementation as this article does not focus on the rho-calculus but merely uses it, but the implementation can be designed without our extensions.\\

Since the blockchain protocol is often used in systems where security is a major concern, verifying that the security can not be breached is very relevant. One such aspect is the integrity of the chain.
Integrity is an important aspect of the blockchain protocol, as one concept of the blockchain algorithm is the modification to the chain by adding new blocks.\\

In this article we will present a type system to verify the integrity of a blockchain protocol implemented in the rho-calculus. The article will first discuss the extensions to the rho-calculus, thereafter present the rules of the type system. After that we will prove that the type system ensures that the integrity of the protocol can not be broken. Finally the type system is applied to part of our blockchain implementation. The full description of our blockchain implementation is in the appendix.
